---
title: 'Getting a Functionnal-Structural Plant Model into a comprehensive R pipeline:'
author: "Adrien Heymans, Felicien Meunier, and Guillaume Lobet"
date: "`r format (Sys.time(), '%B, %Y')`"
output:
  pdf_document:
    fig_caption: yes
header-includes:
  - \usepackage{subfig}
subtitle: MARSHAL-pipeline
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/GitHub/marshal-pipeline")
```

***

# Introduction

**MARSHAL**, the MAize Root System Hydraulic Architecture soLver that combines a root architecture model, CRootBox [@CRootBox], the water flow equation resolution algorithm of Doussan et al. (1998) [@Doussan], improved by including the analytical solution of Landsberg and Fowkes [-@Landsberg1978] extended for root systems [@Meunier2017-ue] and the macroscopic parameter calculation of Couvreur et al. [@Couvreur2012]. MARSHAL calculates root system conductance, 1 to 3-D uptake distribution and other upscaled variables (plant leaf water potential or transpiration) for any combination of structural and functional traits of maize.

## How to use MARSHAL in a R environment

To run this example, the `marshal package is required. This package can be found on [GitHub](https://github.com/MARSHAL-ROOT/marshal).
Or by simply execute the following line in the R environment:

```{r echo=TRUE, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("MARSHAL-ROOT/marshal")
library(marshal)
```

MARSHAL is built upon a handful of other packages that need to be loaded. One additional set of [function](https://github.com/MARSHAL-ROOT/marshal-pipeline/R/) has to be loaded manually.
```{r preambule, echo=T, warning=F, message=F}
library(data.table)
library(Matrix)
library(tidyverse)
library(readxl)
library(cowplot)
library(xml2)
library(knitr)
`%!in%` <- compose(`!`, `%in%`)
source("R/io_function.R")
```
```{r, eval=T, echo= F, warning=FALSE, message=F}
library(marshal)
```

```{r eval= T, echo= F}
babbel <- c("all_rain" = "rain all time",
           "Zea_mays_1_Leitner_2010" = "Leitner 10", 
           "Zea_mays_3_Postma_2011" = "Postma 11", 
           "Zea_mays_4_Leitner_2014"=  "Leitner 14", 
           "1" = "1", "2"= "2", "3"="3", "4" = "4", "5"="5",
           "10" = "10", "20" = "20", "30" = "30", "40" = "40",
           "50" = "50", "60"= "60",
           "Doussan et al." = "Doussan et al.", "Early Doussan et al." = "Early",
           "Late Doussan et al." = "Late",
           "type_1" = "Axes", "type_2" = "Lateral",
           "-300" = "humid", "-7000" = "dry", "-15000" = "arid")
```

# Boundary condition of MARSHAL.

The inputs of MARSHAL are :

- The hydraulic properties of the roots.
- The water potential of the soil.
- The root system architecture.
- The initial pressure strength that pull water out of the collar (boundary condition).

To illustate the potential of MARSHAL, we created a series of 27 scenarios, from three root system architecture (RSA) examples, three different hydraulics properties of the roots, and three vertical distribution of the soil water potential due to three drying coefficients ($3 soil \times 3 RSA \times 3 hydraulic conductivities$).

## Hydraulic properties of the root system

The hydraulic conductivities of the root system can be found in the litterature, by measuring it on root samples or with the helps of modelling tools. Here, the conductivities of the root come from the Doussan et al. paper [-@Doussan]. To show some possibilities, three scenarios in total were built from this Doussan et al. table of conductivities (figure \ref{conduct}). The first, is the original values placed along the root axes from the apex. The second, is based on the first but the maturity of the root anatomy is advanced of 5 cm towards the apex. And the third, is the opposite of the second, or in other words, the maturity of the root anatomy, insted of being advance towards the apex, is moved of 5 cm backwards.

### The conductivities of the different root type.

```{r BC conductivities, warning= F, echo=F}
# Conductivities from Doussan et al. 1998
conductivities <- read_excel("www/conductivities.xlsx") 

# Creating scenarios of Conductivities similar to the Doussan et al. 1998
# at the exeption of all changes of conductivities have been move forward or backward to
# the tip.
conduct_1 <- conductivities%>%
  mutate(scenario = "Doussan et al.")
conduct_2 <- conductivities%>%
  mutate(scenario = "Early Doussan et al.")
conduct_2$x[which(conduct_2$x %!in% c(0, 100))] <- conduct_2$x[which(conduct_2$x %!in%
                                                                       c(0, 100))]-5
conduct_3 <- conductivities%>%
  mutate(scenario = "Late Doussan et al.")
conduct_3$x[which(conduct_3$x %!in% c(0, 100))] <- conduct_3$x[which(conduct_3$x %!in%
                                                                       c(0, 100))]+5
conductivities <- rbind(conduct_2, conduct_1, conduct_3)
```

```{r fig.cap= "Conductivities properties on axes and lateral root type. \\label{conduct}", results = 'asis', warning= F, echo=F, fig.pos="h",  fig.subcap= c("Axial conductance.", "Radial conductivity."), fig.scap=NA, out.width='.40\\linewidth', fig.width=4, fig.height=4,fig.show='hold',fig.align='center'}

# Evolution of Kx along the root types
conductivities %>%
  filter(type == "kx",
         order_id == 1 | order_id == 2) %>% 
  ggplot(aes(x,y, colour = factor(scenario)))+
  geom_line(aes(color = factor(scenario), linetype = factor(scenario)))+
  theme_classic()+
  xlab("distance from the tips (cm)") +
  ylab("Axial conductance (cm4 hPa-1 d-1)")+
  guides(colour = F,
         linetype = F)+
  #labs(colour = "Conductivity \nscenarios",
  #     linetype = "Conductivity \nscenarios")+
  facet_wrap(~order, scales = "free", labeller =as_labeller(babbel))

#Evolution of Kr along the root types
conductivities %>%
  filter(type == "kr",
         order_id == 1 | order_id == 2) %>% 
  ggplot(aes(x,y, colour = factor(scenario)))+
  geom_line(aes(color = factor(scenario), linetype = factor(scenario)))+
  theme_classic()+
  xlab("distance from the tips (cm)")+
  ylab("Radial conductivity (cm hPa-1 d-1)")+
  labs(colour = "Conductivity \nscenarios",
       linetype = "Conductivity \nscenarios")+
  theme(legend.position = "top", legend.direction = "vertical" )+
  facet_wrap(~order, scales = "free", labeller =as_labeller(babbel))

```

## Root system architecture with CRootBox

Modelling root system architecture can be achieved with CRootBox [@CrootBox]. Some examples of the parameter files for a couples of specieses are details in the *modelparameter* folder, which is linked to the [CRootBox repository](https://github.com/Plant-Root-Soil-Interactions-Modelling/CRootBox).

For the purpose of the example we choose to work with three parameter files of maize: 

- *Zea_mays_3_Postma_2011*
- *Zea_mays_1_Leitner_2010*
- *Zea_mays_4_Leitner_2014*

The following lines of code allows to create five unique root system architectures for each parameter files. It computes the root growth during 60 days and load every ten days the architecture information in a data table. The time resolution can be increased inside the CRootBox implementation, if needed. For the implementation of this example, the root growth has been restricted to the below ground level for a more realistic point of view. Furthermore, some segments were not build up to the whole root system because they were shorter than the spatial resolution of the root system.

```{r all_roots, eval=T, echo=T, warning=F, message= F}
# Number of repetion per root system architecture example
nrep <- 5

# List of three CrootBox parameter files for corn
param_choise <- c("Zea_mays_1_Leitner_2010",
                  "Zea_mays_3_Postma_2011",
                  "Zea_mays_4_Leitner_2014")

all_roots <- NULL
for(param_name in param_choise){
  # Load param of the selected example
  rparam <- read_rparam(path = paste0("./www/", param_name, ".rparam"))
  pparam <- read_pparam(path = paste0("./www/", param_name, ".pparam"))
  # Overwrite the param files that will be use
  write_rparam(rparam, "./www/param.rparam")
  write_pparam(pparam, "./www/param.pparam")
  
  for(i in c(1:nrep)){
  ################## 
  #  Run CRootBox  #
  ##################
    if(Sys.info()['sysname'] == "Darwin"){
        system("chmod 777 www/a-mac.out")
        system("www/a-mac.out")
    }
    else if(Sys.info()['sysname'] == "Windows"){
        system("www/a.exe")
    }
    else if(Sys.info()['sysname'] == "Linux"){
      system("chmod 777 www/a.out")
      system("www/a.out")
    }
    else{
      message("An error occured, which depended of your
operating system. If so, please compile CRootBox on
your device. The instruction can be found: 
https://github.com/MARSHAL-ROOT/marshal-pipeline/tree/master/17_06%20CRootBox")
    }

  # Get all the .txt files exported by CRootBox
  fls <- list.files("./")
  fls <- fls[grepl("rootsystem.txt", fls)]
  
  for(f in fls){
    temp <- fread(f, header = T)
    temp$age <- strsplit(f, "_")[[1]][1]
    temp$rep <- i
    temp$ex <- param_name
    # Save the temporary data in a permanent file to use.
    all_roots <- rbind(all_roots, temp)
    }
  }
}

```

```{r , eval= F}
# Saving the root system information in a .csv
write_csv(all_roots, "all_roots.csv")

# To gain time once you have a all_roots.csv file created
# Loading the .csv file can be achieve with:
all_roots <- read.csv("all_roots.csv")
```

The figure \ref{roots} shows the root system architectures that comes out CRootBox at half of the simulation time (30 days).

```{r fig.cap="Projection in two dimentions of the different root systems computed with CRootBox at the age of 30 days \\label{roots}", echo=FALSE, fig.pos = "h", fig.height=3, fig.width = 7}
all_roots%>%
  filter(age == "30",
         rep < 6) %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2), alpha = 0.2, size = 0.2)+
  geom_hline(yintercept = 0, color = "tan3")+
  facet_grid(ex ~ rep, labeller = as_labeller(babbel))
```

### Architectural phenes

Once the complete root system architecture is computed there are a number of architetural phenes that we can accessed, such as:

- the area of the convex hull
- the rooting depth
- the root length density along the soil profile
- the number of individual roots per root system
- the total length of the root system
- ...

#### The convex hull

The convex hull area is a classical root system descriptor. It gives a qualitative information about root exploration.

```{r Convex hull, warning=F}
root_20 <- all_roots%>%
  filter(age %in% c("20","40","60")) 
pol_ch = poly_area<- NULL
for(i in unique(all_roots$ex)){
  for(j in unique(all_roots$rep)){
    for(ag in unique(root_20$age)){
      for(xy in c("x", "y")){# get the convex hull from two sides
    tmp <- root_20%>%
      filter(ex == i, rep == j, age == ag)%>%
      select(paste0(xy,"2"),z2, ex, rep, age)
      # select(x2,z2, ex, rep, age)
    first_col <- tmp[,1]
    x <- matrix(c(first_col, tmp$z2), nc = 2)
    # Get the incices of the unique points lying on the convex hull
    ch <- chull(x= first_col, y = tmp$z2)
    ch <- c(ch, ch[1])
    
    # Area of the convex hull
    xy.coords <- cbind(first_col, tmp$z2)
    chull.coords <- xy.coords[ch,]
    chull.poly <- sp::Polygon(chull.coords, hole = F)
    chull.area <- chull.poly@area

    polyg <- cbind(as.data.frame(x[ch,]), ex = i, rep = paste0(j,xy), age = ag)
    pol_area <- c(chull.area/10000)%>% # Transformation into square meter
                    as.tibble()%>%
                    transmute(area = value, ex = i, rep= paste0(j,xy), age = as.numeric(ag))
    poly_area <- rbind(poly_area, pol_area)
    pol_ch <- rbind(pol_ch, polyg)
      }
    }
  }
}

```


```{r , echo = F, fig.cap="Area of the convex hull for the different root system architecture examples. $\\bigtriangleup$ = Postma 2011, $\\square$ = Leitner 2014, and $\\bigcirc$ = Leitner 2010 RSA example", fig.subcap=c("Superposition of all the convex hull repetitions.", "The area of each convex hull."), fig.pos = "h", out.width='.45\\linewidth', fig.width=3, fig.height=3,fig.show='hold',fig.align='center'}
pol_ch%>%
  ggplot()+
  theme_classic()+
  coord_fixed() +
  geom_polygon(aes(x = V1, y = V2, fill = factor(rep)), alpha = 0.2)+
  ylab("depth (cm)")+
  xlab("L (cm)")+
  facet_grid(ex ~ age, labeller =as_labeller(babbel))+
  guides(fill = F)
  #labs(fill = "repetitions")+
  #theme(legend.position="bottom")

poly_area%>%
  ggplot(aes(x = as.factor(age), y = area))+
  theme_classic()+
  geom_boxplot(aes(fill = ex), alpha = 0.2)+
  geom_jitter(aes(shape = ex, colour = ex), size = 2, width = 0.1, height = 0, alpha = 0.5)+
  ylab("area (m²)")+
  xlab("time (d)")+
  #labs(colour = "RSA example",
  #     shape = "RSA example")+
  guides(fill = F,
         colour = F,
         shape = F)

```

#### The maximal rooting depth

Thanks to the detailled information coming from CRootBox, it is possible to measure some root phenes along the z axis. The maximal rooting depth is a interesting phenotypic values. This can be use in other models such as Feddes et al. [-@feddes1978] to estimate root water uptake.

```{r graph density, echo=T}
# Summarise the total root length and the rooting depth information. 
RLD <- all_roots%>%
  mutate(age = as.numeric(age))%>%
  group_by(age, rep, ex)%>%
  summarise(root = sum(length),
            rooting_depth = min(z2))

RLD2 <- all_roots%>%
  mutate(age = as.numeric(age))%>%
  group_by(age, rz1 = round(z1/2)*2, # on every two cm of the profile  
           ex)%>%
  summarise(root = sum(length)/nrep)
```

```{r rooting depth, echo=F, fig.cap="Rooting depth of the different root system examples", fig.pos = "h", fig.height=2.5}

RLD %>%
  ggplot(aes(age, rooting_depth))+
  geom_point(aes(shape= ex, colour = ex),size = 2, alpha = 0.5)+
  geom_point(aes(x = 0, y = -3, colour = ex, shape = ex), size = 2, alpha = 0.5)+ # seeds
  geom_hline(yintercept = 0, color = "tan3")+
  theme_classic()+
  facet_wrap(~ex, labeller =as_labeller(babbel))+
  labs(colour = "RSA example", shape = "RSA example")+
  ylab("Rooting depth (cm)")+
  xlab("time (day)")

```

#### Root length density

Root length density is a major phenotypic trait mesured in field when below ground information are needed In this case the total root length is computed every ten days.

```{r root length, echo= F, warning= F, message= F, fig.cap="The root lenght", fig.subcap=c("The total root length", "The root length density after 60 days."), fig.pos = "h", out.width='.49\\linewidth', fig.width=3, fig.height=3,fig.show='hold',fig.align='center'}
RLD %>%
  ggplot(aes(age, root/1000, colour = factor(ex)))+
  geom_smooth(alpha = 0.5)+
 # geom_point(aes(x = 0, y = 0), size = 2)+
  theme_classic()+
 # facet_wrap(~ex, labeller =as_labeller(babbel))+
  guides(colour = F)+
  #labs(colour = "RSA example")+
  ylab("Total root length (m)")+
  xlab("Time (d)")

RLD2%>%
  filter(age == 60)%>%
  ggplot(aes(rz1, root, colour=ex)) + 
  geom_line(alpha = 0.5) +
  geom_smooth(se=F, method = "loess") +
  theme_classic()+
  coord_flip() + 
  xlab("depth (cm)") +
  ylab("length (cm)")+
  theme(legend.position = "top", legend.direction = "vertical" )+
#  facet_wrap(~ex, labeller = as_labeller(babbel))+
  labs(colour = "RSA example")
```

## The water soil potential

The pressure head of the water potential within the soil is created from the followig line of code.
Here, there are three soil scenarios with three different coefficients for the drying function.

The drying function is :

 $\psi_{i}$ = $\alpha \times \frac{(Z_i+L)^{10} \times T_{i}}{L^{10} \times T_{end}} -230$ 
 
- $\psi_{i}$ = water potential in the soil at i cm below the surface.
- $\alpha$ = drying coefficient of the soil (-300 = "humid", -7000 = "dry" and -15.000 = "arid").
- $Z_{i}$ = the depth (cm)
- $L$ = the maximal soil profile depth.
- $T$ = the simulation time (day)
- -230 is the water potential in the soil at the field cappacity for a silty soil.

```{r plot water soil potential}
# Take the same time variable as the one that were implemented in CRootBox.
full_time <- sort(unique(as.numeric(all_roots$age)))
time_step = full_time[2]-full_time[1]
endTime = max(full_time)
ntimesteps = endTime/time_step

# Creating some values for the water potential in the soil along the profile depth.
profile_depth <- 150
z <- seq(-profile_depth, 0, by = 5)
value <- sort(rep(full_time, length(z)))
psi <- rep(-230, length(value))
z <- rep(z, ntimesteps)

soil <- NULL
# Making three scenarios
for(i in c(-300, -7000, -15000)){
soil_tmp <- cbind(z, value, psi)%>%
  as.tibble()%>%
  mutate(psi = i*(((z+profile_depth)^(10))*value)/
           ((profile_depth^10)*endTime)-230,
         humid = i)
soil_tmp <- soil_tmp%>%
  mutate(id = 1:nrow(soil_tmp))
soil<- rbind(soil, soil_tmp)
}
```

```{r , echo=F, fig.cap="Water potential evolution during the simultaion time along the soil profile", fig.pos = "!h", fig.height=2.5}
soil %>%
  filter(value %in% c(10,30,50,60))%>%
  ggplot(aes(psi, z, colour = factor(value)))+
  geom_point(alpha = 0.7)+
  theme_classic()+
  xlab("Pressure head (hPa)") +
  ylab("Depth (cm)")+
  labs(colour = "Time (days)")+
  facet_grid(~humid, labeller =as_labeller(babbel))+
  theme(axis.text.x=element_text(angle=90))
```

## The water potential at the collar

Expressed in hecto-Pascal, the pressure head define the transpiration strenght that pulls the water out of the root system. here we take the default value of $-15.000 \ hPa$

```{r}
# Water potential at the collar (hPa)
tpots <- -15000
```

# MARSHAL

MARSHAL provides an estimation of the conductance of the whole root system as well as the actual and the potential transpiration (based on the soil profile).
Here we call the MARSHAL function `getSUF` that will solve the hydraulic part of the root system for each soil, conductivities, root system architecture scenarios and at each time step of the process.


```{r new_all_roots MARSHAL, eval=T, echo=T, warning=F, message= F}

new_all_roots <- NULL
results<- NULL
k <- 1
# Computing the root system hydraulic architecture
# Loop to run MARSHAL with the selected simulation parameters.
for(exa in unique(all_roots$ex)){# Example of RSA
  for(re in unique(all_roots$rep)){ # repetition
    for(ag in sort(as.numeric(unique(all_roots$age)))){# age of the RS
      for(sen in unique(conductivities$scenario)){ # hydraulic properties
        for(hum in unique(soil$humid)){ # Scenario of water potential in the soil
        
        # Select specific Soil for the simulation
        temp_soil <- soil %>% 
          filter(value == ag,
                 humid == hum)%>% 
          select(-value, -humid)
        # Select specific root system for the simulation
        temp_root <- all_roots %>% 
          filter(age == ag,
                 rep == re,
                 ex == exa)%>%
          as.tibble()%>%
          select(-ex)
        # Select specific conductivities
        temp_conduct <- conductivities%>%
          filter(scenario == sen)%>%
          select(-scenario)
        
        # -----------------------------
        # Run MARSHAL
        # -----------------------------
        hydraulics <- getSUF(temp_root, 
                             temp_conduct, 
                             temp_soil, 
                             hetero = T, 
                             Psi_collar = tpots)
        
        # Aggregate output from MARSHAL
        results <- rbind(results, data.frame(krs = hydraulics$krs, 
                                             tact = hydraulics$tact, 
                                             tpot = hydraulics$tpot, 
                                             tp = tpots,
                                             scenario = sen,
                                             age = ag,
                                             rep = re,
                                             ex = exa,
                                             humid = hum,
                                             simulation = k))
        
        # Keep the information about the very detail hydrological parameter on
        # all the root segment only for one repetion of the plant per simulation.
        if(re >= nrep-1){
        # Format dataset to be compatible with MARSHAL output
        first <- temp_root[temp_root$node1ID == 0,]
        nodals_ids <- unique(temp_root$branchID[temp_root$type == 4 | 
                                                  temp_root$type == 5])
        for(no in nodals_ids){
          temp <- temp_root%>%
           filter(branchID == no)
          temp <- temp[1,] 
          connection <- data.frame(node1ID = 0,
                             node2ID = temp$node1ID,
                             branchID = temp$branchID,
                             x1 = first$x1, y1 = first$y1, z1 = first$z1,
                             x2 = temp$x1, y2 = temp$y1, z2 = temp$z1,
                             radius = temp$radius,
                             length = sqrt((first$x1-temp$x1)^2 + 
                                             (first$y1-temp$y1)^2 + 
                                             (first$z1-temp$z1)^2 ),
                             R = 0, G = 0, B = 0,
                             time = temp$time,
                             type = temp$type,
                             age = temp$age,
                             rep = temp$rep)
          new_table = rbind(temp_root, connection)
          temp_root = new_table
          }
        temp_root <- temp_root[order(temp_root$node2ID, decreasing = F),]
        
        # Merge output of MARSHAL on specific root segment
        temp_root$suf <- as.vector(hydraulics$suf)
        temp_root$suf1 <- as.vector(hydraulics$suf1)
        temp_root$kx <- as.vector(hydraulics$kx)
        temp_root$kr <- as.vector(hydraulics$kr)
        temp_root$jr <- as.vector(hydraulics$jr)
        temp_root$psi <- as.vector(hydraulics$psi)
        temp_root$jxl <- as.vector(hydraulics$jxl)
        temp_root$psi_soil <- as.vector(hydraulics$psi_soil)
        # Add the simulation specificity to the dataset
        temp_root$scenario <- sen
        temp_root$ex <- exa
        temp_root$humid <- hum
        temp_root$rep <- re
        new_all_roots <- rbind(new_all_roots, temp_root)
        }
        k <- k + 1
        }
      }
    }
  }
}
```

```{r, eval= F}
# Save the results
write_csv(new_all_roots, "new_all_roots.csv")
# Load the saved results
new_all_roots <- read.csv("new_all_roots.csv")
```
```{r, echo=F}
# The previous process altered the age information. 
new_all_roots <- new_all_roots%>%
  mutate(age = as.numeric(age)*10)

```

# Results :

Once the hydraulic part has been associated to each root segment and the macroscopic properties have been computed, we can visualize them in different ways.

### Standard uptake fraction (SUF)

The Standard Uptake Fraction (SUF) is the relative distribution of root water uptake between root segments when water is equally available in space (units: %) [@Couvreur2012].

```{r suf on roots, echo=FALSE, fig.cap="Standard uptake fraction of the different root systsem architecture", fig.pos = "h", fig.height= 4}

new_all_roots%>%
  filter(age == 60,
         rep == nrep,
         humid == min(humid),
         scenario == "Doussan et al.") %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = log10(suf1)), alpha = 0.8, size = 0.3)+
  facet_grid( ~ ex, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  labs(colour = "log(SUF) (-)")+
  ylab("Depth (cm)")

```

One of the major advantage of the SUF is to estimate where should be the segments which contribute to the water uptake of the plant. Here we focuces on the smallest regions on which 50% of the water uptake occurs in a soil where the water potential is homogenous along the profile.


```{r}
fif <- NULL
for (exa in 1:length(param_choise)) {
fi <-  new_all_roots%>%
  filter(age == 60,
         rep == nrep,
         scenario == "Doussan et al.",
         humid == min(humid),
         ex == param_choise[exa])%>%
  mutate(or_suf = sort(suf1, decreasing = T))

i <- 1
k <- 0
while(k <= 0.5){
  k <- k + fi$or_suf[i]
  i <- i + 1
}
fif <- rbind(fif, c(ex = param_choise[exa], suf = fi$or_suf[i]))%>%
  as.tibble()%>%
  mutate(suf = as.numeric(suf))
}
```

```{r suf1 on Postma 2011 rsa, echo=FALSE, fig.cap="The smallest region on the root system hydraulic architecture which contains 50 % of the SUF", fig.pos = "!h", fig.height=4}

# Postma 2011
fifty_p1 <- new_all_roots%>%
  filter(age == 40,
         rep == nrep,
         scenario == "Doussan et al.",
         suf1 >= fif$suf[2],
         ex == param_choise[2])

# Leitner 2010
fifty_l0 <- new_all_roots%>%
  filter(age == 40,
         rep == nrep,
         scenario == "Doussan et al.",
         suf1 >= fif$suf[1],
         ex == param_choise[1])

# Leitner 2014
fifty_l4 <- new_all_roots%>%
  filter(age == 40,
         rep == nrep,
         scenario == "Doussan et al.",
         suf1 >= fif$suf[3],
         ex == param_choise[3])

new_all_roots%>%
    filter(age == 40,
         rep == nrep,
         scenario == "Doussan et al.")%>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2), alpha = 0.01)+
  geom_segment(data = fifty_l0, aes(x = x1, y = z1, xend = x2, yend = z2, colour = suf1))+
  geom_segment(data = fifty_l4, aes(x = x1, y = z1, xend = x2, yend = z2, colour = suf1))+
  geom_segment(data = fifty_p1, aes(x = x1, y = z1, xend = x2, yend = z2, colour = suf1))+
  facet_wrap(~ex, ncol = 3, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  ylab("Depth (cm)")
```

```{r jr on roots, echo=FALSE, error= F, warning=F, fig.cap="Absorption speed, comparison between the RSA and the soil scenario", fig.pos = "!h", fig.height=4}
new_all_roots%>%
  filter(age == 60,
         rep == nrep,
         scenario == "Doussan et al.") %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = log10(jr)), alpha = 0.8, size = 0.2)+
  facet_grid(ex ~ humid, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  labs(colour = "Radial fluxes \nlog10(cm³/day)")+
  ylab("Depth (cm)")
```

```{r jxl on roots, echo=FALSE, warning=F, error= F, fig.cap="Absorption speed, comparison between the RSA and the soil scenario", fig.pos = "!h", fig.height=4}

new_all_roots%>%
  filter(age == 60,
         rep == nrep,
         scenario == "Doussan et al.")%>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = log10(jxl)), alpha = 0.8, size = 0.2)+
  facet_grid(ex ~ humid, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  labs(colour = "Axial fluxes \nlog10(cm³/day)")+
  ylab("Depth (cm)")
```

```{r kr on roots, echo=FALSE, warning = F, fig.cap="The radial conductivity (Kr) on root segment, comparison between the different conductivity scenario and main root system architecure examples", fig.pos = "!h", fig.height=4}

new_all_roots%>%
  filter(age == 60,
         rep == nrep) %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = kr), alpha = 0.8, size = 0.2)+
  facet_grid(ex~scenario, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  ylab("Depth (cm)")
```

```{r kx on roots, echo=FALSE, warning = F, fig.pos = "h", fig.cap="The axial conductance (Kx) on root segment, comparison between the different conductivity scenario and main root system architecure examples", fig.height=4}

new_all_roots%>%
  filter(age == 60,
         rep == nrep) %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = kx), alpha = 0.8, size = 0.2)+
  facet_grid(ex~scenario, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  ylab("Depth (cm)")
```

```{r evolution jr on roots, echo=FALSE, warning=F, fig.pos = "h", fig.cap = "Absorption dynamics due to different soil scenarios on the Postma root system architecture example", fig.height=4}

new_all_roots%>%
  filter(rep == nrep,
         scenario == "Doussan et al.",
         ex == unique(new_all_roots$ex)[2],
         age <= 40) %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = log(jr)), alpha = 0.8, size = 0.2)+
  facet_grid(humid ~ age, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  ylab("Depth (cm)")

```

```{r evolution of jxl on roots, echo=FALSE, warning=F, fig.pos = "h", fig.height=4}

new_all_roots%>%
  filter(rep == nrep,
         scenario == "Doussan et al.",
         ex == unique(new_all_roots$ex)[2],
         age <= 40) %>%
  ggplot()+
  theme_classic()+
  coord_fixed() + 
  geom_segment(data = , aes(x = x1, y = z1, xend = x2, yend = z2, colour = log(jxl)), alpha = 0.8, size = 0.3)+
  facet_grid(humid ~ age, labeller = as_labeller(babbel)) + 
  scale_color_viridis_c()+
  ylab("Depth (cm)")

```

To look at the different hydraulic marco-properties along the profile depth, we took the mean values of the variable total on every two centimeters. 

```{r dens}
# For the two repetions on which we have values on each segment,
# we take the mean values of the sum of each variables.  
dens <- new_all_roots%>%
  mutate(age = as.numeric(age))%>%
  group_by(type, age, rz1 = round(z1/2)*2, # on every two cm of the profile  
           scenario, ex, humid)%>%
  summarise(root = sum(length)/2, # The mean of the sum on the two repetitions
            su = sum(suf)/2,
            sud = sum(suf/length)/2,
            su1 = sum(suf1)/2,
            j = sum(jr)/2,
            jx = sum(jxl)/2,
            p = sum(psi)/2,
            kr = sum(kr)/2)
```

```{r graph dens root, echo = F, warning=F, fig.cap="Root length density", fig.pos = "!h", fig.height= 4}
dens%>%
  filter(age == 60,
         scenario == "Doussan et al.",
         humid == min(humid))%>%
  ggplot(aes(rz1, root, colour=factor(type))) + 
  geom_line(alpha = 0.5) +
  geom_smooth(se=F, method = "loess") +
  theme_classic()+
  coord_flip() + 
  xlab("depth (cm)") +
  ylab("length (cm)")+
  facet_wrap(~ex, labeller = as_labeller(babbel))+
  labs(colour = "Root type")

```

```{r dens suf 1, echo = F, warning=F, fig.cap="Evolution of the SUF with Leitner 2010 RSA parameter", fig.pos = "!h", fig.height=4}
dens%>%
  filter(ex == unique(dens$ex)[1],
         scenario == "Doussan et al.",
         age > 10)%>%
  ggplot(aes(rz1, su1, colour=factor(type)))+ 
  geom_line(alpha = 0.8) +
  #geom_smooth(se=F, alpha = 0.1) +
  coord_flip() + 
  theme_classic()+
  xlab("Depth (cm)") +
  ylab("Standard uptake fraction (-)")+
  labs(colour = "Root type")+
  theme(axis.text.x=element_text(angle=90)) +
  facet_grid(~age, labeller = as_labeller(babbel))

```

```{r dens suf 2, echo = F, warning=F, fig.cap="Evolution of the SUF with Postma 2011 RSA parameter", fig.pos = "!h", fig.height=4}
dens%>%
  filter(ex == unique(dens$ex)[2],
         scenario == "Doussan et al.",
         age > 10)%>%
  ggplot(aes(rz1, su1, colour=factor(type))) + 
  geom_line(alpha = 0.8) +
  #geom_smooth(se=F, alpha = 0.1) +
  coord_flip() +
  theme_classic()+
  xlab("Depth (cm)") +
  ylab("Standard uptake fraction (-)")+
  labs(colour = "Root type")+  
  theme(axis.text.x=element_text(angle=90)) +
  facet_grid(~age)

```

```{r dens suf 3, echo = F, warning=F, fig.cap="Evolution of the SUF with Leitner 2014 RSA parameter", fig.pos = "!h", fig.height=4}
dens%>%
  filter(ex == unique(dens$ex)[3],
         scenario == "Doussan et al.",
         age > 20)%>%
  ggplot(aes(rz1, su1, colour=factor(type))) + 
  geom_line(alpha = 0.8) +
  #geom_smooth(se=F, alpha = 0.1, method = "gam") +
  coord_flip() +   
  theme_classic()+
  xlab("Depth (cm)") +
  ylab("Standard uptake fraction (-)")+
  labs(colour = "Root type")+
  theme(axis.text.x=element_text(angle=90)) +
  facet_grid(~age)

```

```{r dens radial 2, echo = F, fig.cap="Comparison of the radial fluxes between the different soil scenarios and the root system architectures", fig.pos = "!h", fig.height=4}
dens%>%
  filter(age == 60,
         scenario == "Doussan et al."
         #,ex == unique(dens$ex)[1]
         )%>%
  ggplot(aes(rz1, j, colour=factor(type))) + 
  geom_line(alpha = 0.8) +
  #geom_smooth(se=F) +
  coord_flip() +  
  theme_classic()+
  xlab("Depth (cm)") +
  ylab("Radial fluxes (cm³/j)")+
  labs(colour = "Root type")+
  theme(axis.text.x=element_text(angle=90)) +
  facet_grid(ex~humid,  scales = "free", labeller = as_labeller(babbel))
```

```{r dens axial 2, fig.cap="Comparison of the axial fluxes between the different soil scenarios and the root system architectures", fig.pos = "!h", fig.height=4}
dens%>%
  filter(age == 40,
         scenario == "Doussan et al.")%>%
  ggplot(aes(rz1, jx, colour=factor(type))) + 
  geom_line(alpha = 0.7) +
  #geom_smooth(se=F) +
  coord_flip() +   
  theme_classic()+
  xlab("Depth (cm)") +
  ylab("Axial fluxes (cm³/j)")+
  labs(colour = "Root type")+
  facet_grid(ex~humid, scales = "free", labeller = as_labeller(babbel))
```

```{r psi, echo=F, warning= F, fig.cap="Water pressure head at the soil-root interface", fig.pos = "!h", fig.height=4}
dens%>%
  filter(age == 50,
         scenario == "Doussan et al.")%>%
  ggplot(aes(rz1, p, colour=factor(type))) + 
  geom_line(alpha = 0.8) +
  #geom_smooth(se=F) +
  coord_flip() +  
  theme_classic()+
  xlab("Depth (cm)") +
  ylab("psi (hPa)")+
  labs(colour = "Root type")+
  theme(axis.text.x=element_text(angle=90)) +
  facet_grid(humid~ex, labeller = as_labeller(babbel))
```

```{r krs, echo = F, warning = F, fig.cap="Evolution of the whole root system conductance. Effect comparison between root system architecture and root conductivity modification.", fig.pos = "!h", fig.height=4.2, fig.width= 8}
results%>%
  ggplot(aes(x= age, y = krs, colour = factor(ex)))+
  geom_point(aes(shape = factor(scenario)),size = 2, alpha = 0.5)+
  geom_smooth(aes(linetype = factor(scenario)), alpha = 0.02, method = "loess")+
  xlab("Time (d)") +
  ylab("Root system conductance (cm3 hPa-1 d-1)")+
  labs(colour = "Root architecture example",
       shape = "scenario",
       linetype = "scenario")
```

```{r transp, warning= F}
Transpiration<- results%>%
  mutate(humid = as.character(humid))%>%
  group_by(age, rep, scenario, humid, ex)%>%
  summarise(Tpot = max(tpot, tact),
            Tact = min(tpot, tact))
```

```{r transpi with water, echo = F, warning= F, fig.pos = "!h", fig.height=4, fig.cap="Evolution of the transpiration rate in a wet soil."}

Transpiration%>%
  filter(humid == "-300")%>%
  ggplot(aes(x= age, y = Tact, colour = factor(ex)))+
  geom_point(aes(shape = factor(scenario)),size = 2, alpha = 0.5)+
  geom_smooth(aes(x = age, y = Tpot, colour = factor(ex),
                  linetype = factor(scenario)), alpha = 0.01, method = "loess")+
  theme_classic()+
  xlab("Time (d)") +
  ylab("Transpiration (cm³/day)")+
  labs(colour = "Root architecture example")+  labs(colour = "RSA example",
       shape = "scenario",
       linetype = "scenario")
```


```{r transpi with dry condition, echo = F, warning = F, fig.pos = "!h", fig.height=4, fig.cap="Evolution of the transpiration rate in two different soil scenarios where the soil is drying up."}

Transpiration%>%
    filter(humid %in% c("-7000", "-15000"))%>%
  group_by(ex, humid, age, scenario, rep)%>%
  summarise(Tact = mean(Tact),
            Tpot = mean(Tpot))%>%

  ggplot(aes(x= age, y = Tact, colour = factor(ex)))+
  geom_point(aes(shape = factor(scenario)),size = 2.5, alpha = 0.4)+
  geom_smooth(aes(x = age, y = Tpot, colour = factor(ex),
                linetype = factor(scenario)), alpha = 0.5, se = F, method = "loess")+
  geom_hline(yintercept = 0)+
  theme_classic()+
  xlab("Time (d)") +
  ylab("Transpiration (cm³/day)")+
  labs(colour = "RSA example")+  labs(colour = "RSA example",
       shape = "scenario",
       linetype = "scenario")+
  facet_wrap(~humid, labeller = as_labeller(babbel))

```

# References
